\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Kuruva Naveen Kumar} % Your name
\address{Srisailam,Nandyaldistrict,Andhrapradesh} 
\address{(+91)9740433934 \\ kuruvanaveenkumar2001@gmail.com}

\begin{document}

\begin{rSection}{Education}


{\bf Presidency University,yelahanka,Bangalore} \hfill {\em August 2018 - June 2022} 
\\ Bachelor of Engineering, Computer.\hfill { Overall CGPA: 7.76 }

\end{rSection}

\begin{rSection}{Career Objective}
 To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
\end{rSection}

\begin{rSection}{Projects}
{\bf GitHub Notifier}
\\Online food ordering system (08/2020 - 11/2020)
Our main project is to speed up the Food Service ordered by customers. One of the objective is to save the time which is very important now a days. The system reduces much of human efforts. This project is to develop an application which gives provision to the restaurant owners to flourish their business by uploading menu at no cost.

{\bf GitHub Notifier}
\\Air quality monitoring project using Iot (02/2021 - 05/2021) 
measuring air quality.

\end{rSection}

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages \ & C, Python\#  \\
Technologies & HTML5, CSS\\
Python Robertic Framework  \\
Databases & MySql\\
Manual Testing , Smoke Testing , UI Testing , Unit Testing, Automation Testing , Functional Testing , API Testing, Regression Testing , API Automation \\
Quality Engineering , Quality Assurance \\
\end{tabular}

\end{rSection}
% 
% 
% \newpage
\begin{rSection}{Work Experience}
\begin{rSubsection}{Talent Recruit Software Pvt. Ltd, India}{Jun 2022 - Present}{Software QA Engineer}{}
 \item Performed Manual, API, Database Testing across different modules in the new SaaS ATS.
 \item Successfully implemented new processes across team: created test quality metrics, training materials, organized on-boarding, improving work processes for production defects.
 \item Mentored QA engineers, providing guidance, assigning tasks and reviewing Test Scenarios for manually perform of smoke and regression tests
 \item Created common API testing Framework using Postman
 \item Automated API Testing and integrated it with Database and UI automation - Robot Framework
 \item Implemented Agile Methodology process in the project
 \item Organized presentations and demos by the end of Release to stakeholders and customers
\end{rSubsection}

\end{rSection}
% 



\end{document}
